MachLLensFinder - I: A Machine Learning Strong Lensing Identification Pipeline

### 2016-08-04 ms.tex
Latest changes, some new sketch in Methodology section.

>>>>

%-------------------------------------------------%
\subsubsection{Histogram Oriented Gradients}
%-------------------------------------------------%
Histogram oriented gradients (HOG) is a feature extraction method that
computes centered horizontal and vertical gradients with no smoothing.
Originally created for human detection, .... This computes the
gradient orientation and magnitudes in an image by first dividing the
image into $n\times n$ blocks of X\% overlap.  The gradient
orientation is then quantized into m bins. ``(optional) global image
normalisation computing the gradient image in x and y computing
gradient histograms normalising across blocks flattening into a
feature vector''\citep{dalalandtriggs_05}.

% Need to look into edge orientation histograms, scale-invariant
% feature transform descriptors, shape contexts.

% NEED TO FEED THE DESCRIPTORS TO SOMETHING WITH SUPERVISED LEARNING.
% (e.g. SVM, Neural network).

%-------------------------------------------------%
\subsection{Logistic Regression}
%-------------------------------------------------%

% Regularization coefficient:
% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html
